### 2024-04-29 Presentations/Conferences etc/UKCI 2024/Paper/output/paper.tex
Updating logs etc.
Updating log files and applying changes to .tex file, which changed the size of some images

    \keywords{Machine Learning, Deep Learning, Embedded Systems, The Edge, Neural Networks, Arduino}
\end{abstract}

@@

\begin{figure}[ht]
\includegraphics[width=8.5cm, height=6cm]{images/data_collection_system.png}
\centering
\caption{Arduino Nano 33 BLE Sensor Development Kit}
\label{fig:collection2}
\end{figure}

@@

Using Python the two datasets were brought together into a single \texttt{DataFrame}. The data was then into training and testing datasets using \texttt{train\_test\_split} with the default settings.

The results of this analysis can be seen in Fig. \ref{fig:init_binary}
\begin{figure}[ht]
\includegraphics[width=8cm, height=3cm]{images/initial_binary_search.png}
\centering
\caption{Results, Shown as a Percentage, for the Initial Binary Search}
\label{fig:init_binary}
\end{figure}

@@

\begin{figure}[ht]
\includegraphics[width=8cm, height=3cm]{images/initial_analysis_gridsearch.png}
\centering
\caption{Results, shown as a Percentage Value for the Grid Search}
\label{fig:initial_analysis_gridsearch}
\end{figure}

@@

\begin{figure}[ht]
\includegraphics[width=8cm, height=7cm]{images/new_data_results.png}
\centering
\caption{Results for the Initial Binary Search}
\label{fig:new_data_results}
\end{figure}

@@

\begin{figure}[ht]
\includegraphics[width=8cm, height=1cm]{images/nn_settings.png}
\centering
\caption{Optimal Setting for Neural Network}
\label{fig:nn_settings}
\end{figure}

>>>>

\keywords{Machine Learning, Deep Learning, Embedded Systems, The Edge, Neural Networks, Arduino}
% \keywords{\mbox{Machine Learning}, \mbox{Deep Learning}, \mbox{Embedded Systems}, \mbox{The Edge}, \mbox{Neural Networks}, \mbox{Arduino}}
\end{abstract}

@@

\begin{figure}[ht]
\includegraphics[width=10cm, height=6cm]{images/data_collection_system.png}
\centering
\caption{Arduino Nano 33 BLE Sensor Development Kit}
\label{fig:collection2}
\end{figure}

@@

Using Python the two datasets were brought together into a single \texttt{DataFrame}. The data was then into training and testing 
datasets using 
\texttt{train\_test\_split} with the default settings. The results of this analysis can be seen in Fig. \ref{fig:init_binary}

\begin{figure}[ht]
\includegraphics[width=12cm, height=3.5cm]{images/initial_binary_search.png}
\centering
\caption{Results, Shown as a Percentage, for the Initial Binary Search}
\label{fig:init_binary}
\end{figure}

@@

\begin{figure}[ht]
\includegraphics[width=12cm, height=3.5cm]{images/initial_analysis_gridsearch.png}
\centering
\caption{Results, shown as a Percentage Value for the Grid Search}
\label{fig:initial_analysis_gridsearch}
\end{figure}

@@

\begin{figure}[ht]
\includegraphics[width=12cm, height=8cm]{images/new_data_results.png}
\centering
\caption{Results for the Initial Binary Search}
\label{fig:new_data_results}
\end{figure}

@@

\begin{figure}[ht]
\includegraphics[width=12cm, height=2cm]{images/nn_settings.png}
\centering
\caption{Optimal Setting for Neural Network}
\label{fig:nn_settings}
\end{figure}
